Output Summary

### 2023-08-16 03-post-process/ms-content/ms-content.Rmd

---
output: 
  pdf_document:
    keep_tex: true
params:
  scenario:
    label: "Scenario"
    value: "base_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  beta_fig:
    value: TRUE
  relationship_fig:
    value: TRUE
  no_fall_fig:
    value: TRUE
  surv_compare_fig:
    value: TRUE
  apportion_compare_fig:
    value: TRUE
  corr_compare_fig:
    value: TRUE
header-includes:
  - \usepackage{sansmathfonts}
  - \usepackage{helvet}
  - \renewcommand{\rmdefault}{\sfdefault}
  - \usepackage{float}
  - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
  - \captionsetup{width=\textwidth}
editor_options: 
  chunk_output_type: console
---

@@

corr_compare_caption = "
  Correlation terms of the covariance matrices controlling process variability.
  Posterior means of population pair-specific correlations are displayed as points, and the posterior of the average of the 6 pairs is summarized in black (thin lines are 95% CRIs, thick lines 50% CRIs, and cross marks are means).
  Survival processes are denoted by $x \\to y$, where as transition processes are denoted by $\\Pr(x)$.
  The correlation in survival processes representing the migration downstream and upstream through the mainstem (LGR $\\to$ BON and BON $\\to$ LGR, respectively) represent among-origin correlation, hence the lack of points.
"
```

@@

@@

```{r corr-compare-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(corr_compare_caption), eval = params$corr_compare_fig}

>>>>

---
output: 
  pdf_document:
    keep_tex: true
params:
  scenario:
    label: "Scenario"
    value: "base_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    value: FALSE
  beta_fig:
    value: FALSE
  relationship_fig:
    value: TRUE
  no_fall_fig:
    value: TRUE
  surv_compare_fig:
    value: TRUE
  apportion_compare_fig:
    value: TRUE
  corr_compare_fig:
    value: TRUE
  WUL_change_fig:
    value: TRUE
header-includes:
  - \usepackage{sansmathfonts}
  - \usepackage{helvet}
  - \renewcommand{\rmdefault}{\sfdefault}
  - \usepackage{float}
  - \usepackage[labelfont={bf,sc},labelsep=period]{caption}
  - \captionsetup{width=\textwidth}
editor_options: 
  chunk_output_type: console
---

@@

corr_compare_caption = "
  Correlation terms of the covariance matrices controlling process variability.
  Posterior means of population pair-specific correlations are displayed as points, and the posterior of the average of the 6 pairs is summarized in black (thin lines are 95% CRIs, thick lines 50% CRIs, and cross marks are means).
  Survival processes are denoted by $x \\to y$, where as transition processes are denoted by $\\Pr(x)$.
  The correlation in survival processes representing the migration downstream and upstream through the mainstem (LGR $\\to$ BON and BON $\\to$ LGR, respectively) represent among-origin correlation, hence the lack of points.
"

WUL_change_fig_caption = "
  Density-dependent survival relationships from egg (panels a-d) and parr (panels e-f) to smolt arriving at Lower Granite Dam (LGR) under current (solid lines) and increased (dashed lines) weighted usable habitat (WUL).
  Egg $\\to$ LGR survival includes density effects that are both direct (e.g., egg survival varies as a function of egg density) and indirect (parr size varies as a function of egg density, and survival varies with size), whereas parr $\\to$ LGR survival includes only the indirect density effects.
"
```

@@

```{r corr-compare-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(corr_compare_caption), eval = params$corr_compare_fig, time_it = TRUE}

```{r WUL-change-fig, fig.width = 7.2, fig.height = 4.5, eval = params$WUL_change_fig, fig.cap = WUL_change_fig_caption, time_it = TRUE}

prep_samples = function(j) {

  # the parameters needed to calucate process model expected values
  the_params = c("alpha[pop]", "beta[pop]", "^lambda$",
                 "omega0[pop]", "omega1[pop]", "mu_pi[1,pop]",
                 "gamma0[1,pop]", "gamma1[1,pop]",
                 "gamma0[2,pop]", "gamma1[2,pop]",
                 "theta0[pop]", "theta1[pop]",
                 "tau0[pop]", "tau1[pop]"
  )

  # extract the posterior samples for all of these parameters for this population
  the_samps = post_subset(post, sub_index(the_params, pop = j), matrix = TRUE)

  # handle the names
  the_names = postpack:::drop_index(names(the_samps[1,]))
  the_names[which(the_names == "gamma0")] = paste0("gamma0", c("_fall", "_spring"))
  the_names[which(the_names == "gamma1")] = paste0("gamma1", c("_fall", "_spring"))
  colnames(the_samps) = the_names

  return(the_samps)
}

prep_sample = function(the_samps, i, j) {
  c(the_samps[i,],
    WUL = unname(jags_data$wul[j]),
    E_scale = unname(jags_data$E_scale),
    L_Pb_scale = unname(jags_data$L_Pb_scale[j]),
    L_Pb_center = unname(jags_data$L_Pb_center[j]),
    L_Mb_scale = unname(jags_data$L_Mb_scale[j]),
    L_Mb_center = unname(jags_data$L_Mb_center[j])
    )
}

get_phi_hat = function(x, E, WUL_change = 0, start = "E") {
  with(as.list(c(x, E = E, WUL_change = WUL_change)), {
    beta_hat = lambda * WUL

    WUL_new = WUL * (1 + WUL_change)
    beta_hat_new = lambda * WUL_new
    beta_new = beta_hat_new * (beta/beta_hat)

    phi_E_Pb = 1/(1/alpha + E/beta_new)
    Pb = E * phi_E_Pb

    L_Pb = exp(omega0 + omega1 * log((E/E_scale)/WUL_new))
    L_Pb_star = (L_Pb - L_Pb_center)/L_Pb_scale

    Pa_fall = Pb * mu_pi
    Pa_spring = Pb * (1 - mu_pi)

    phi_Pa_Mb_fall = plogis(gamma0_fall + gamma1_fall * L_Pb_star)
    phi_Pa_Mb_spring = plogis(gamma0_spring + gamma1_spring * L_Pb_star)

    Mb_fall = Pa_fall * phi_Pa_Mb_fall
    Mb_spring = Pa_spring * phi_Pa_Mb_spring

    Delta = exp(theta0 + theta1 * L_Pb_star)

    L_Mb = L_Pb * Delta
    L_Mb_star = (L_Mb - L_Mb_center)/L_Mb_scale

    phi_Mb_Ma = plogis(tau0 + tau1 * L_Mb_star)

    Ma_fall = Mb_fall * phi_Mb_Ma
    Ma_spring = Mb_spring * phi_Mb_Ma
    Ma = Ma_fall + Ma_spring

    if (start == "E") out = Ma/E
    if (start == "Pb") out = Pb/E
    return(out)
  })
}

get_phi_hat_post = function(j, E_pred, WUL_change = 0, start = "E") {

  the_samps = prep_samples(j = j)

  out = sapply(1:nrow(the_samps), function(i) {
    x = prep_sample(the_samps, i = i, j = j)
    sapply(E_pred, function(e) get_phi_hat(x, E = e, WUL_change = WUL_change, start = start))
  })

  out = t(out)
  colnames(out) = paste0("var", 1:ncol(out))

  postpack::post_convert(cbind(postpack:::id_mat(post), out))
}

get_phi_real_post = function(j, start = "E") {

  if (start == "E") start_param = "^E[.+,pop]"
  if (start == "Pb") start_param = "^Pb[.+,pop]"

  Ma_fall = post_subset(post, sub_index("^Ma[.+,1,1,pop]", pop = j), matrix = TRUE)
  Ma_spring = post_subset(post, sub_index("^Ma[.+,2,1,pop]", pop = j), matrix = TRUE)
  start_out = post_subset(post, sub_index(start_param, pop = j), matrix = TRUE)

  phi = (Ma_fall + Ma_spring)/start_out

  colnames(phi) = paste0("var", 1:ncol(phi))
  postpack::post_convert(cbind(postpack:::id_mat(post), phi))
}

plot_f = function(j, start, WUL_change) {
  phi_real_post = get_phi_real_post(j = j, start = start)
  phi_real = post_summ(phi_real_post, ".")
  E_real = post_summ(post, sub_index("^E[.+,pop]", pop = j))
  E_pred = seq(min(E_real["mean",]), max(E_real["mean",]), length = 30)

  phi_hat_post = get_phi_hat_post(j = j, E_pred, start = start)
  phi_hat = post_summ(phi_hat_post, ".")
  phi_hat_new_post = get_phi_hat_post(j = j, E_pred, WUL_change = WUL_change, start = start)
  phi_hat_new = post_summ(phi_hat_new_post, ".")

  plot(phi_real["mean",] ~ E_real["mean",], type = "n",
       ylim = make_lim(0, phi_hat[c("2.5%","97.5%"),],
                phi_hat_new[c("2.5%","97.5%"),]),
                # phi_real["mean",]),
       # ylim = make_lim(0, ifelse(start == "E", 0.075, 0.3)),
       xlim = c(0, max(E_real["mean",], E_pred)),
       xaxt = "n")

  # points(phi_real["mean",] ~ E_real["mean",], pch = 21, 
  #        col = "black", bg = scales::alpha("grey25", 0.25), cex = 0.8)

  polygon(x = c(E_pred, rev(E_pred)), 
          y = c(phi_hat["2.5%",], rev(phi_hat["97.5%",])),
          col = tranp_col, border = NA)
  lines(phi_hat["mean",] ~ E_pred, lwd = 2)
  lines(phi_hat["2.5%",] ~ E_pred)
  lines(phi_hat["97.5%",] ~ E_pred)

  polygon(x = c(E_pred, rev(E_pred)), 
          y = c(phi_hat_new["2.5%",], rev(phi_hat_new["97.5%",])),
          col = tranp_col, border = NA)
  lines(phi_hat_new["mean",] ~ E_pred, lwd = 2, lty = 2)
  lines(phi_hat_new["2.5%",] ~ E_pred,  lty = 2)
  lines(phi_hat_new["97.5%",] ~ E_pred, lty = 2)
  at_x = axisTicks(par("usr")[1:2], log = FALSE)
  axis(side = 1, at = at_x, labels = at_x/1e6)
  panel_label(paste0("(", letters[ifelse(start == "E", 0, 3) + j], ") ", pops[j]))

  if (j == 1) {
    if (start == "E") {
      axis_labels(ylab = "Egg \u2192 LGR Survival", outer = FALSE, yline = 1)
      legend("topright", title = "WUL", legend = c("Current", paste0("\u2191", WUL_change * 100, "%")), lty = c(1,2), seg.len = 1.5, bty = "n", cex = 0.8)
    } 
    if (start == "Pb") axis_labels(ylab = "Parr \u2192 LGR Survival", outer = FALSE, yline = 1)
  }

}

mypar(mfrow = c(2,4), col.axis = "black")
junk = sapply(1:4, function(j) plot_f(j, "E", 1))
junk = sapply(1:4, function(j) plot_f(j, "Pb", 1))
axis_labels(xlab = "Egg Production (Millions)")
```

@@
